Ceph Parallel File System Evaluation Report

### 2013-08-23 introduction.tex
Add spider2 references

National Center for Computational Sciences (NCCS) runs one of the largest HPC
storage system built on top of Lustre parallel file system. The latest
installation of Spider II is designed to operate at over 1 TB/s peak
throughput with 40 PB of raw capacity. As a scratch file system connected to a
leadership computing platform at the scale of Titan, Spider II emphasizes
\textit{capability} over \textit{capacity}. However, we also recognize that
there are a wide variety of scientific data and workloads with different
performance and data access requirements, e.g., RESTful interface, S3-like
API, cloud solution integration, to name a few.

@@

As interesting and feature-rich as Ceph may be, our environment and the sheer
scale of its potential application drive us to first look into its scalability
and performance.  As part of the study, we set up a dedicated testbed within
NCCS for the Ceph file system evaluation. The goal of our study is to
investigate the feasibility of using the Ceph for our future HPC storage
deployment. This paper presents our experience, results, and observations.
While evaluating our results, please keep in mind that Ceph is still a
relatively \textit{young} parallel file system and its code base is changing
rapidly. In between releases, we often experienced different stability and
performance outcomes.  We will try to make clear in the writing when such
changes occurred.

>>>>

National Center for Computational Sciences (NCCS) runs one of the largest HPC
storage system built on top of Lustre parallel file system. The latest
installation of Spider II\cite{spider2} is designed to operate at over 1 TB/s peak
throughput with 40 PB of raw capacity. As a scratch file system connected to a
leadership computing platform at the scale of Titan, Spider II emphasizes
\textit{capability} over \textit{capacity}. However, we also recognize that
there are a wide variety of scientific data and workloads with different
performance and data access requirements, e.g., RESTful interface, S3-like
API, cloud solution integration, to name a few.

@@

As interesting and feature-rich as Ceph may be, our environment and the sheer
scale of its potential application drive us to first look into the all
important scalability and performance aspect of it.  As part of the study, we
set up a dedicated testbed within NCCS for the Ceph file system evaluation.
The goal of our study is to investigate the feasibility of using the Ceph for
our future HPC storage deployment. This paper presents our experience,
results, and observations.  While evaluating our results, please keep in mind
that Ceph is still a relatively \textit{young} parallel file system and its
code base is changing rapidly. In between releases, we often experienced
different stability and performance outcomes.  We will try to make clear in
the writing when such changes occurred.
